### 2018-07-31 Paper/intro.tex
..

%\paragraph{Motivation}
Computing statistical properties of 
complex systems containing uncertain parameters is
challenging due to the need for a large number of expensive model evaluations. 
Surrogate models make such computations possible by replacing 
expensive model runs with cheap evaluations of an approximate model.
%
%Surrogate modeling has become a critical component of scientific computing
%owing to the emergence of the field of uncertainty quantification for
%scientific and engineering applications. 
%
Commonly used approaches for surrogate modeling include polynomial chaos
expansions (PCEs)~\cite{Xiu:2002,Ghanem:2003,Olivier:2010}, multivariate
adaptive regression splines (MARS)~\cite{friedman93}, Gaussian processes
(GPs)~\cite{Rasmussen:2004}, or Kriging~\cite{Stein:2012}, and neural
networks~\cite{Funahashi:1989,Specht:1990}. A pertinent
challenge associated with surrogate construction involves the process of
\textit{training} that typically requires a large number of model runs.  In
situations involving large-dimensional systems and computationally intensive
simulations, the training of a surrogate becomes challenging and
even prohibitive in some cases. A possible approach for mitigating this
challenge involves computation of global sensitivity measures such as Sobol'
indices~\cite{Sobol93} to identify
the \emph{important parameters}---i.e., parameters that predominantly
contribute towards the variability of the model output.

>>>>

%\paragraph{Motivation}
Computing statistical properties of 
complex systems containing uncertain parameters is
challenging due to the need for a large number of expensive model evaluations. 
Surrogate models make such computations possible by replacing 
expensive model runs with cheap evaluations of an approximate model.
%
%Surrogate modeling has become a critical component of scientific computing
%owing to the emergence of the field of uncertainty quantification for
%scientific and engineering applications. 
%
Commonly used approaches for surrogate modeling include polynomial chaos
expansions (PCEs)~\cite{Xiu:2002,Ghanem:2003,Olivier:2010}, multivariate
adaptive regression splines (MARS)~\cite{friedman93}, Gaussian process
(GP) and Kriging models~\cite{Rasmussen:2004,Stein:2012}, and neural
networks~\cite{Funahashi:1989,Specht:1990}. A pertinent
challenge associated with surrogate construction involves the process of
\textit{training} that typically requires a large number of model runs.  In
situations involving large-dimensional systems and computationally intensive
simulations, the training of a surrogate becomes challenging and
even prohibitive in some cases. A possible approach for mitigating this
challenge involves computation of global sensitivity measures such as Sobol'
indices~\cite{Sobol93} to identify
the \emph{important parameters}---i.e., parameters that predominantly
contribute towards the variability of the model output.
